---
title: "STAT 120 Group Activity"
author: "Victor Huang Andrew Weller, Mason Priest, Nora Caballero"
date: "4/28/2021"
output:
  pdf_document: default
  html_document: default
---

1.a The parameter of interest would be the proportions of car that are ineffective.

$H_{0}: p_{mf} = 0.1$ verses $H_{a}: p_{mf} > 0.1$

1.b $\hat{p} = 0.125$

1.c 
pnorm
Type I: They recall all cars even though there is less or equal to ten percent of cars experiencing malfunctions

Type II: They do not recall the cars even though there is more than ten percent of cars experienncing malfunctions

1.d Yes; do not have enough information to draw a conclusion

2.a No; $H_{0}: \mu = 10$ verses $H_{a}: \mu < 10$;$z = -1.43$; $p = 0.076$; we can not be 95% confident in that the average honey production is less than 10 lbs.

2.b 8 plus or minus 6.6402

3.a
```{r, echo=FALSE}
library(CarletonStats)
SleepCaffeine<-read.csv("https://www.lock5stat.com/datasets2e/SleepCaffeine.csv")
boot(Words ~ Group, data = SleepCaffeine, conf.level=0.9)
```
We can be 90% sure that the mean diffence between the caffiene and sleeping groups is between -5.25 and -0.833.

3.b -3 plus minus 7.055632

```{r,echo=FALSE}
qnorm(0.05, -3, 1.362) * 1.34642
```