---
title: "STAT 120 HW 7"
author: "Victor Huang"
date: "5/17/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(Lock5Data)
library(CarletonStats)
opts_chunk$set(echo = FALSE,out.width="50%",fig.align="center",message=FALSE)
```

Section 7.6: Some parts ask you to create quantile-normal plots split by levels of a factor.
The code to do this is right above the exercises (also see the example on pages 76-77).

2

a.

```{r,echo=FALSE}
beerwings <- read.csv("https://math.carleton.edu/Stat120/RLabManual/beerwings.csv")
ggplot(beerwings, aes(x = gender, y = hotwings)) + geom_boxplot()
```


b.

```{r,echo=FALSE}
library(dplyr)
beerwings %>% group_by(gender) %>% summarize (mean(hotwings), sd(hotwings))
ggplot(beerwings, aes(sample = hotwings)) + geom_qq() + geom_qq_line() + facet_grid(. ~ gender)
```
From the graph, one can see that there are some clear outliers to the rough line prescribed by the graph. As such, a normal distribution may not be appropriate and normality may not be met.

c.

```{r,echo=FALSE}
t.test(hotwings ~ gender, data = beerwings)
```
We can conclude that there is a difference in the average number of hotwings consumed between males and females. This is assuming that the data does not match a normal distribution.

d.

```{r,echo=FALSE}
library(CarletonStats)
permTest(hotwings ~ gender, data = beerwings)
```
As one can see, we reach the same conclusion

3

a.
```{r,echo=FALSE}
facesymmetry <- read.csv("https://math.carleton.edu/Stat120/RLabManual/facesymmetry.csv")
t.test(facesymmetry$l.pupil, alt="greater")
```
From the data displayed above, we fid a 95 confidence interval between 31.62929 to Inf.

b.

Since we get the right and left eye measurements from the same person, this would be a matched-pair setting.

```{r,echo=FALSE}
facesymmetry <- read.csv("https://math.carleton.edu/Stat120/RLabManual/facesymmetry.csv")
eyesdiff <- facesymmetry$l.pupil - facesymmetry$r.pupil
t.test(eyesdiff, alt = "greater")
```
From the data showed above, we get a 95% confidence interval from -0.5277 to Inf.

c.

This is an independent sample setting
```{r,echo=FALSE}
t.test(eyesdiff ~ eye, data = facesymmetry, alt="greater")
```
From the data above, we see that on symmetry does indeed depend on eye dominance.

d.

```{r,echo=FALSE}
t.test(eyesdiff ~ hand, data = facesymmetry, alt="greater")
```
Likewise, we see a 95% confidence interval from -1.691 to inf. As such, we also see that symmetry does indeed depend on hand dexterity (left or right handed).

4

a.

```{r,echo=FALSE}
Sodexho <- read.csv("https://math.carleton.edu/Stat120/RLabManual/Sodexho.csv")
ggplot(Sodexho, aes(x = Type, y = Protein)) + geom_boxplot()
```

b.

```{r,echo=FALSE}
library(dplyr)
Sodexho %>% group_by(Type) %>% summarize (mean(Protein), sd(Protein))
ggplot(Sodexho, aes(sample = Protein)) + geom_qq() + geom_qq_line() + facet_grid(. ~ Type)
```

From the graph, one can see that there are some clear outliers to the rough line prescribed by the graph. As such, a normal distribution may not be appropriate and normality may not be met.

c.

```{r,echo=FALSE}
t.test(Protein ~ Type, data = Sodexho)
```
As we can clearly see from the data, the mean for meat protein is  26.95217 whereas vegetarian protein is only 13.2944. As such, we conclude that the means are not the same

d.
```{r,echo=FALSE}
t.test(Protein ~ Type, data = Sodexho, subset = -c(15,38))
```
Even after getting rid of the outliers, we still come to the same conclusion as before.

e.
```{r,echo=FALSE}
library(CarletonStats)
permTest(Protein ~ Type, data = Sodexho)
```
Looking at the data we see that we can reach the same conclusion as above.

Section 7.1

7.4

$p_{1}$ = 280

$p_{2}$ = 40

$p_{3}$ = 40

$p_{4}$ = 40

7.11

a.

$(210 + 732 + 396 + 125 + 213 + 324)(0.35) = 700$

b.

$\frac{(732 - 700)^2}{700} = 1.46$

c.

$df = 6 - 1 = 5$

7.14

$\chi^2 = \frac{(Actual - Expected)^2}{Expected} = \frac{(66 - 39.67)^2}{39.67} + \frac{(39 - 39.67)^2}{39.67} + \frac{(14 - 39.67)^2}{39.67} = 34.0980$

Looking at our $\chi^2$ value, we can say that there are proportions that aren't the $\frac{1}{3}$ outcome we expect, we find that the win count for rock and scissors don't match the one-third win rate

7.16

$df = 5 - 1 = 4$

Confidence Level: 5%

$\chi^2 = \frac{(Actual - Expected)^2}{Expected} = \frac{(391 - 410)^2}{410} + \frac{(257 - 280)^2}{280} + \frac{(156 - 130)^2}{130} + \frac{(89 - 70)^2}{70} + \frac{(107 - 110)^2}{110} = 13.2087$

p-value = 0.010

Summarizing our data, we can conclude that the data given by the article is not accurate.

7.26

$\chi^2 = \frac{(Actual - Expected)^2}{Expected} = \frac{(357.588 - 345)^2}{357.588} + \frac{(209.088 - 197)^2}{209.088} + \frac{(148.5 - 170)^2}{170} + \frac{(115.236 - 126)^2}{115.236} + \frac{(93.852 - 101)^2}{93.852} + \frac{(79.596 - 72)^2}{79.596} + \frac{(68.904 - 69)^2}{68.904} + \frac{(60.588 - 51)^2}{60.588} + \frac{(54.648 - 57)^2}{54.648} = 9.0876$

p-value = 0.3350

Summarizing out data, we see that our data is not consistent with Benford's Law. 